Assessing Virulence by MCG

### 2017-06-29 doc/RMD/MCG-virulence.Rmd
Add a summary table for severity

```{r vis, fig.width = 5, fig.height = 4}
ggplot(top_mcg, aes(x = MCG, y = Severity)) +
  geom_boxplot() +
  geom_point(position = position_jitter(width = 0.25), alpha = 0.5) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  labs(list(
    title = "Severity for the top 10 MCGs",
    caption = "MCG = Mycelial Compatibility Group"
    ))
```

>>>>

```{r vis, fig.width = 5, fig.height = 4}
set.seed(2017-06-29)
ggplot(top_mcg, aes(x = MCG, y = Severity)) +
  geom_boxplot() +
  geom_point(position = position_jitter(width = 0.25), alpha = 0.5) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  labs(list(
    title = "Severity for the top 10 MCGs",
    caption = "MCG = Mycelial Compatibility Group"
    ))
```

```{r virulence_table}
top_mcg %>% 
  group_by(MCG) %>%
  summarize(N = n(), 
            `Min Severity` = min(Severity),
            `Max Severity` = max(Severity),
            `Average Severity` = mean(Severity)
            ) %>%
  knitr::kable(digits = 2)
```
